Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 300\,pc Halo

### 2021-02-24 cluster_paper/ms.tex
cluster paper: manuscript

A brief
note on terminology.  Low-density stellar associations connected to a
dense population (the ``core'') have been described as ``halos'',
``strings'', ``coronae'', ``snakes'', and ``tidal tails'' \citep[{\it
	e.g.},][]{davenport_death_2010,kounkel_untangling_2019,roser_hyades_2019,tian_discovery_2020,meingast_2021}.
The latter term implies a particular model for the
formation of the association.  We opt to use ``halo'' because it is
concise and model agnostic.  It suffers however from the suggestion of
spherical symmetry.  The halo of NGC\,2516 is anything but.

@@

We chose the stars to focus on based on previously reported
memberships of NGC\,2516, available in the literature.  While a number
of pre-Gaia catalogs were available, the purity and accuracy of the
Gaia-derived results are expected to be the current state of the art.
We therefore adopted what we viewed as the most interesting clustering
samples to compare: those of \citet{cantatgaudin_gaia_2018}
(\citetalias{cantatgaudin_gaia_2018}) and
\citet{kounkel_untangling_2019}
(\citetalias{kounkel_untangling_2019})\footnote{A third sample was
also recently reported by \citet{meingast_2021}. Although the results
of this study were made publicly available too late to be included in
our analysis,  1577 of the 1860 \citet{meingast_2021} sources (85\%)
were included in the \citet{kounkel_untangling_2019} sample.  A
complete set of \cn\ members could very well include some of the newly
reported candidate members from \citet{meingast_2021}.}. While we
could have performed our own clustering analysis based on the Gaia
data, such an effort would be replicating the work of these
investigators. And why would our clustering methods be better than
theirs? We opt instead to use their studies as starting points.

>>>>

A brief note on terminology.  Low-density stellar associations
connected to a dense population (the ``core'') have been described as
being in ``halos'', ``strings'', ``coronae'', ``snakes'', ``the
outskirts'', and ``tidal tails'' \citep[{\it
e.g.},][]{davenport_death_2010,kounkel_untangling_2019,roser_hyades_2019,tian_discovery_2020,meingast_2021}.
The latter term implies a particular model for the formation of the
association.  We opt to use ``halo'' because it is concise and model
agnostic.  It suffers however from the suggestion of spherical
symmetry.  The halo of NGC\,2516 is anything but.

@@

We selected candidate \cn\ members based on those available in the
literature.  While a number of pre-Gaia catalogs were available, the
purity and accuracy of the Gaia-derived results are expected to be the
current state of the art.
We therefore adopted what we viewed as the most interesting clustering
samples to compare: those of \citet{cantatgaudin_gaia_2018}
(\citetalias{cantatgaudin_gaia_2018}) and
\citet{kounkel_untangling_2019}
(\citetalias{kounkel_untangling_2019})\footnote{A third sample was
also recently reported by \citet{meingast_2021}. Although the results
of this study were made publicly available too late to be included in
our analysis,  1577 of the 1860 \citet{meingast_2021} sources (85\%)
were included in the \citet{kounkel_untangling_2019} sample.  A
complete set of \cn\ members could very well include some of the newly
reported candidate members from \citet{meingast_2021}.}.  A useful
visualization of these samples is available online\footnote{
  \url{https://homepage.univie.ac.at/stefan.meingast/coronae.html},
  made by \citet{meingast_2021}.  }.
While we could have performed our own clustering analysis based on the
Gaia data, such an effort would be replicating the work of these
investigators. And why would our clustering methods be better than
theirs? We opt instead to use their studies as starting points.
